---
title: "simpleRegress"
author: "Bessie Luevano"
date: "Summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

I am going to model the length of a bear based on chest size.

```{r}
mychest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(mychest)
summary.lm(mychest)
```

I have two models and in mychest model I used chest to get the length of the bear whereas the first model, simp used the neck to get the length. In mychest model the adjusted r square is 0.7869 and the residual standard error is 4.939. In the simp model the adjusted r squared was 0.7476 and the residual standard error was 5.376. Therefore it appears using the model mychest is a better model to use becuase it explains more of the error and its residual standard error is smaller. 


